Make any stupid plot you want

### 2021-02-19 draft/sections/implementation.tex
stacked bar

\begin{minted}{python}
class Bar(mcollections.Collection):
    def __init__(self, data, transforms, orientation, *args, **kwargs):
        # parameter of the graphic
        self.orientation = orientation 
        super().__init__(*args, **kwargs)
        self.data = data
        self.transforms = transforms

@@

    def draw(self, renderer, *args, **kwargs):
        view = self.data.view(self.axes)
        visual = utils.convert_transforms(view, self.transforms)  
        self.assemble(visual)
        super().draw(renderer, *args, **kwargs)

\end{minted}
The \mintinline{python}{draw} method is the same as the one in the artist example~\ref{code:artist}, but here the visual transformations are factored out into a separate function. This is because in bar we support a rudimentary version of the complex \plus operator such that we can specify multiple components to map to the same visual encoding without requiring th components to be individually specified in the \mintinline{python}{transforms} dictionary. The implementation of this support is slightly more complicated than the simple case, but not in a way that is useful for understanding the framework. The \mintinline{python}{assemble} function constructs bars and sets their edge color to black. Defaults are provided for 'width' and 'floor' to make this function more reusable. Typically the defaults are used for the type of chart shown in figure~\ref{fig:code_bar_simple}, but these visual variables are often set when building composite versions of this chart type as discussed in section~\ref{sec:code_case_study}.

@@

where \mintinline{python}{__init__} can validate that the output of the \vchannel\ is a valid element of the \vfiber\ component the \vchannel\ function is targeting. Creating a callable class also provides a simple way to swap out the specific (data, value) mapping without having to reimplement the validation or conversion logic. A test for equivariance can be implemented trivially such that it is independent of data or encoder.
\begin{minted}{python}
def test_nominal(values, encoder):
    m1 = list(zip(values, encoder(values)))
    random.shuffle(values)
    m2 = list(zip(values, encoder(values)))
    assert sorted(m1) == sorted(m2)
\end{minted}
In this example, \mintinline{python}{is_nominal} checks for equivariance of permutation group actions by applying the encoder to a set of values, shuffling values, and checking that (value, encoding) pairs remain the same. This equivariance test can be implemented as part of the artist or encoder, but for minimal overhead, the equivariant it is implemented as part of the library tests.

>>>>

\begin{minted}{python}
class Bar(mcollections.Collection):
    def __init__(self, data, transforms, orientation = 'v', *args, **kwargs):
        # parameter of the graphic
        self.orientation = orientation 
        super().__init__(*args, **kwargs)
        self.data = data
        self.transforms = transforms

@@

\end{minted}
The \mintinline{python}{draw} method is the same as the one in the artist example~\ref{code:artist} so is ommitted here.  This bar underpins a rudimentary version of the complex \plus operator such that we can specify multiple components to map to the same visual components without requiring th components to be individually specified in the \mintinline{python}{transforms} dictionary. The implementation of this support is slightly more complicated than the simple case, but not in a way that is useful for understanding the framework. The \mintinline{python}{assemble} function constructs bars and sets their edge color to black. Defaults are provided for 'width' and 'floor' to make this function more reusable. Typically the defaults are used for the type of chart shown in figure~\ref{fig:code_bar_simple}, but these visual variables are often set when building composite versions of this chart type as discussed in section~\ref{sec:code_case_study}.

@@

where \mintinline{python}{__init__} can validate that the output of the \vchannel\ is a valid element of the \vfiber\ component the \vchannel\ function is targeting. Creating a callable class also provides a simple way to swap out the specific (data, value) mapping without having to reimplement the validation or conversion logic. A test for equivariance can be implemented trivially
\begin{minted}{python}
def test_nominal(values, encoder):
    m1 = list(zip(values, encoder(values)))
    random.shuffle(values)
    m2 = list(zip(values, encoder(values)))
    assert sorted(m1) == sorted(m2)
\end{minted}
but is currently factored out of the artist for clarity. In this example, \mintinline{python}{is_nominal} checks for equivariance of permutation group actions by applying the encoder to a set of values, shuffling values, and checking that (value, encoding) pairs remain the same. This equivariance test can be implemented as part of the artist or encoder, but for minimal overhead, the equivariant it is implemented as part of the library tests.
